---
title: "Untitled"
author: "nsj"
date: "25 February 2022"
output: pdf_document
---

```{r message=FALSE,warning=FALSE}
library(ggplot2)
library(dplyr)
library(moderndive)
library(ISLR)
library(skimr)
library(plotly)
library(tidyr)
library(jtools)
library(lubridate)
library(car)
library(GGally)
library(gridExtra)
library(sjPlot)
```

```{r data, echo = FALSE, eval = TRUE, warning = FALSE, message = FALSE}
furniture1 <- read.csv("E:/dataset14.csv")
# Import data set 
```

```{r}
furniture <- furniture1 %>%  
  filter(!(is.na((depth)&is.na((height)&is.na(width)))))
furniture$depth[is.na(furniture$depth)] = mean(furniture$depth,na.rm = TRUE)
furniture$height[is.na(furniture$height)] =mean(furniture$height,na.rm = TRUE)
furniture$width[is.na(furniture$width)] = mean(furniture$width,na.rm = TRUE)
furniture <- furniture %>%
  #drop_na() %>%
  mutate(volume = depth/100 * height/100 * width/100,
         expensive = ifelse(price > 1000,TRUE,FALSE))
# Filter data 
```


#Exploratory Data Analysis
We grouped prices to form a new column of variables, with TRUE for prices above 1000 and FALSE for prices up to 1000. the table below shows summary statistics for the length, width, height and volume of furniture for each price category. The 1,2 are depth, 3,4 are height, 5,6 are width and 7,8 are volume. In the following tables grouped as FALSE are 1, 3, 5 and 7 and grouped as TRUE are 2, 4, 6 and 8.
```{r}
furniture %>%
  select(depth,height,width,volume,expensive) %>%
  group_by(expensive) %>%
  skim() %>%
  transmute(Mean=numeric.mean,SD=numeric.sd, Min=numeric.p0, Q1=numeric.p25, Median=numeric.p50, Q3=numeric.p75, Max=numeric.p100) 
```

```{r}
hist1 <- ggplot(furniture,aes(x = price)) +
  geom_histogram(bins = 30) 
  

hist2 <- ggplot(furniture,aes(x = volume)) +
  geom_histogram(bins = 30) 
  

bar1 <- ggplot(furniture,aes(x = sellable_online)) +
  geom_bar() 
  
bar2 <- ggplot(furniture,aes(x = other_colors)) +
  geom_bar() 

bar3 <- ggplot(furniture, aes(x = expensive,  y = ..prop.., group=sellable_online, fill=sellable_online)) + 
  geom_bar(position="dodge", stat="count") +
  labs(y = "Proportion")

bar4 <- ggplot(furniture, aes(x = expensive,  y = ..prop.., group=other_colors, fill=other_colors)) + 
  geom_bar(position="dodge", stat="count") +
  labs(y = "Proportion")
  
hist1log <- ggplot(furniture,aes(x = log(price))) +
  geom_histogram(bins = 30) 
  

hist2log <- ggplot(furniture,aes(x = log(volume))) +
  geom_histogram(bins = 30) 
  
grid.arrange(hist1, hist2, bar1, bar2,bar3, bar4, hist1log, hist2log, ncol=2)
```

# Formal Data Analysis

##Choosing suitable models

1. choose whether the model is binomial or poisson
```{r}
furniture2 <- furniture %>%
  select(X,item_id,sellable_online,other_colors,volume,expensive)
model1 <- glm(formula = expensive ~ ., family = binomial, data = furniture2)
summary(model1)
model2 <- glm(formula = expensive ~ ., family = poisson, data = furniture2)
summary(model2)
```
Only the volume variable is most significant in both models, and according to the AIC minimum criterion, we choose the Binomial model, AIC=383.19.

2.Choose which model is better: probit, cloglog or logit in Binomial
```{r}
model3 <- glm(formula = expensive ~ ., family = binomial(link = 'cloglog'), data = furniture2)
summary(model3)
model4 <- glm(formula = expensive ~ ., family = binomial(link = 'logit'), data = furniture2)
summary(model4)
model5 <- glm(formula = expensive ~ ., family = binomial(link = 'probit'), data = furniture2)
summary(model5)

```
It is same as the former analysis that only the volume variable is most significant in three models. The logit model is better than others which AIC is the lowest and AIC is 383.19.

Therefor, select price and volume .
```{r}
expensive.volume <- furniture %>% 
  select(expensive,volume)
expensive.volume$expensive <- as.factor(expensive.volume$expensive)
```
boxplot of volume by price to get an initial impression of the data:
```{r}
ggplot(data = expensive.volume, aes(x = expensive, y = volume, fill = expensive)) +
  geom_boxplot() +
  labs(x = "expensive", y = "volume")+ 
  theme(legend.position = "none")
```
final model:
```{r}
model <- glm(expensive ~ volume, data = expensive.volume, 
             family = binomial(link = "logit"))
model %>%
  summary()
print("************************************")
summ(model)
print("************************************")
mod1coefs <- round(coef(model), 2)
confint(model) %>%
  kable()
print("************************************")
mod.coef.logodds <- model %>%
                      summary() %>%
                      coef()
print("************************************")
#confidence interval (lower)
volume.logodds.lower <- mod.coef.logodds["volume", "Estimate"] - 
                      1.96 * mod.coef.logodds["volume", "Std. Error"]
volume.logodds.lower
#confidence interval (lower)
volume.logodds.upper <- mod.coef.logodds["volume", "Estimate"] + 
                      1.96 * mod.coef.logodds["volume", "Std. Error"]
volume.logodds.upper
#95% confidence interval of(2.43,3.81)
plot_model(model, show.values = TRUE, transform = NULL,
           title = "Log-Odds (above 1000)", show.p = FALSE)
#Hence the point estimate for the log-odds is 3.12, which has a corresponding 95% confidence interval of (2.43, 3.81). 
```

```{r}
#add the estimates of the log-odds to our data set:
expensive.volume <- expensive.volume %>%
                  mutate(logodds.T = predict(model))
#simply exponentiate the log-odds:
model %>%
 coef() %>%
  exp()
#95% confidence interval for the odds by simply exponentiating the lower and upper bounds of our log-odds interval:
volume.odds.lower <- exp(volume.logodds.lower)
volume.odds.lower
volume.odds.upper <- exp(volume.logodds.upper)
volume.odds.upper
plot_model(model, show.values = TRUE,axis.lim = c(10,50),
           title = "Odds (above 1000)", show.p = FALSE)
```
```{r}
#add the estimates of the odds to our data set:
expensive.volume <- expensive.volume %>%
                  mutate(odds.T = exp(logodds.T))
#add the probabilities to our data:
expensive.volume <- expensive.volume %>%
                  mutate(probs.T = fitted(model))
#plot the probability of being TRUE:
ggplot(data = expensive.volume, aes(x = volume, y = probs.T)) +
  geom_smooth(method="glm", 
              method.args = list(family="binomial"), 
              se = FALSE) +
  labs(x = "volume", y = "Probability of being T")
plot_model(model, type = "pred", title = "",
            axis.title = c("volume", "Prob. of T"))
```



```{r}
odd1 <- plot_model(model2, show.values = TRUE,
title = "", show.p = TRUE)

odd2 <- plot_model(model3, show.values = TRUE,
title = "", show.p = TRUE)

grid.arrange(odd1, odd2, nrow = 2)
```




















